 

### 2021-06-09 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

Leaf respiration is lower during the day than the night, due to light-induced inhibition that is highest in high-irradiance and moderate-to-high-temperature and lowest at high-irradiance and low-temperature [@atkinLeafRespirationSnow2000; @atkinLeafRespirationSnow2000; @keenanWidespreadInhibitionDaytime2019; @zaragoza-castellsDoesGrowthIrradiance2007]. Light-induced inhibition of leaf respiration influences $Q_{10}$ where $Q_{10}$ is greater in the in the dark, and decreases with increase in irradiance [@atkinLeafRespirationSnow2000].

>>>>

Leaf respiration is lower during the day than the night, due to light-induced inhibition that is highest in high-irradiance and moderate-to-high-temperature and lowest at high-irradiance and low-temperature [@atkinLeafRespirationSnow2000; @keenanWidespreadInhibitionDaytime2019; @zaragoza-castellsDoesGrowthIrradiance2007]. Light-induced inhibition of leaf respiration influences $Q_{10}$ where $Q_{10}$ is greatest in the dark, and decreases with increase in irradiance [@atkinLeafRespirationSnow2000].
